---
title: "Exercises"
output:
  html_document:
    toc: yes
    theme: readable
    #number_sections: yes
    code_folding: hide
    toc_depth: 2
    toc_float: yes
    css: slides/www/style.css
  #html_notebook:
  #  toc: yes
  #  theme: readable
  #  #number_sections: yes
  #  code_folding: hide
  #  toc_depth: 3
  #  toc_float: yes
editor_options:
  markdown:
    wrap: 140
---

# Exercises Session I

## charts {.tabset .tabset-pills}
### plotly

There are two ways to make use of plotlys framework.  

[ggplotly](https://plotly.com/ggplot2/) & [plotly for R](https://plotly.com/r/)
ggplotly turns your ggplot graphs with the function *ggplotly()* into an interactive graph. 

plotly uses a different syntax style, but provides more interactive capabilities

```{r echo=TRUE, message=FALSE, warning=FALSE, size= "100%"}
library(plotly)
library(broom)
library(dplyr)
data(diamonds, package = "ggplot2")

data <- sample_n(diamonds, 300)

modlss <- loess(price ~ carat, data = data)
fit <- arrange(augment(modlss,se_fit = TRUE), carat)

p <- ggplot(NULL, mapping = aes(x = carat, y = price )) +
              geom_ribbon(data  = fit, mapping = aes(ymin = .fitted - 2*.se.fit, ymax = .fitted + 2*.se.fit), fill = "grey70")+
              geom_point(data = data, alpha = 0.7, mapping = aes(size = depth, group = cut, color = cut)) +
              geom_line(data = fit, aes(x = carat, y = .fitted)) 
  


ggplotly(p)
```

 
### highcharter 

The main difference in ggplot2's geom_ functions and hc_add_series is that we need to add data and aesthetics explicitly in every function while in ggplot2 one can add data and aesthetics in a layer and then can further add more geoms which can work on same data and aesthetics.

An accurate example is given below using the diamond dataset in the ggplot2 package.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(highcharter)
library(broom)
library(dplyr)
data(diamonds, package = "ggplot2")

data <- sample_n(diamonds, 300)

modlss <- loess(price ~ carat, data = data)
fit <- arrange(augment(modlss,se_fit = TRUE), carat)

highchart() %>%
  hc_add_series(data, type = "scatter",
                hcaes(x = carat, y = price, size = depth, group = cut)) %>%
  hc_add_series(fit, type = "line", hcaes(x = carat, y = .fitted),
                name = "Fit", id = "fit") %>%
  hc_add_series(fit, type = "arearange",
                hcaes(x = carat, low = .fitted - 2*.se.fit,
                      high = .fitted + 2*.se.fit),
                linkedTo = "fit")
```

### plot_ly 

The main difference in ggplot2's geom_ functions and hc_add_series is that we need to add data and aesthetics explicitly in every function while in ggplot2 one can add data and aesthetics in a layer and then can further add more geoms which can work on same data and aesthetics.

An accurate example is given below using the diamond dataset in the ggplot2 package.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(plotly)
library(broom)
library(dplyr)
data(diamonds, package = "ggplot2")

data <- sample_n(diamonds, 300)

modlss <- loess(price ~ carat, data = data)
fit <- augment(modlss, se_fit = TRUE)


fig <- plot_ly(data = data, x = ~carat) %>% 
  add_markers(y = ~price, 
              color = ~cut, 
              size = ~carat, 
              text = ~paste("Price: ", price, '$<br>Cut:', cut)) %>%
  add_lines(y = ~fitted(loess(price ~ carat)),
                         line = list(color = 'lightblue'),
                         name = "Loess Smoother") %>%
  add_ribbons(data = augment(loess(price ~ carat,data = data),se_fit = TRUE), 
              ymin = ~.fitted - 2 * .se.fit,
              ymax = ~.fitted + 2 * .se.fit,
              line = list(color = "rgba(2, 162, 182, 0.05)"),
              fillcolor = "rgba(2, 162, 182, 0.2)",
              name = "Standarderror"
              )


fig

# highchart() %>%
#   hc_add_series(data, type = "scatter",
#                 hcaes(x = carat, y = price, size = depth, group = cut)) %>%
#   hc_add_series(fit, type = "line", hcaes(x = carat, y = .fitted),
#                 name = "Fit", id = "fit") %>%
#   hc_add_series(fit, type = "arearange",
#                 hcaes(x = carat, low = .fitted - 2*.se.fit,
#                       high = .fitted + 2*.se.fit),
#                 linkedTo = "fit")
```

## Exercise 1. Layout

Create 

```{r}



library(shiny)

# Define UI ----
ui <- fluidPage(
  titlePanel("My Shiny App"),
  sidebarLayout(
    sidebarPanel(
      h2("Installation"),
      p("Shiny is available on CRAN, so you can install it in the usual way from your R console:"),
      code('install.packages("shiny")'),
      br(),
      br(),
      br(),
      br(),
      img(src = "rstudio.png", height = 70, width = 200),
      br(),
      "Shiny is a product of ", 
      span("RStudio", style = "color:blue")
    ),
    mainPanel(
      h1("Introducing Shiny"),
      p("Shiny is a new package from RStudio that makes it ", 
        em("incredibly easy "), 
        "to build interactive web applications with R."),
      br(),
      p("For an introduction and live examples, visit the ",
        a("Shiny homepage.", 
          href = "http://shiny.rstudio.com")),
      br(),
      h2("Features"),
      p("- Build useful web applications with only a few lines of code—no JavaScript required."),
      p("- Shiny applications are automatically 'live' in the same way that ", 
        strong("spreadsheets"),
        " are live. Outputs change instantly as users modify inputs, without requiring a reload of the browser.")
    )
  )
)

# Define server logic ----
server <- function(input, output) {
  
}

# Run the app ----
shinyApp(ui = ui, server = server)


```

## Exercise 2. Inputs


```{r}

ui <- fluidPage(
  titlePanel("censusVis"),
  
  sidebarLayout(
    sidebarPanel(
      helpText("Create demographic maps with 
               information from the 2010 US Census."),
      
      selectInput("var", 
                  label = "Choose a variable to display",
                  choices = list("Percent White", 
                                 "Percent Black",
                                 "Percent Hispanic", 
                                 "Percent Asian"),
                  selected = "Percent White"),
      
      sliderInput("range", 
                  label = "Range of interest:",
                  min = 0, max = 100, value = c(0, 100))
    ),
    
    mainPanel()
  )
)
```


## Exercise 3. Outputs and Reactives

```{r}
library(shiny)

ui <- fluidPage(
  titlePanel("censusVis"),
  
  sidebarLayout(
    sidebarPanel(
      helpText("Create demographic maps with 
               information from the 2010 US Census."),
      
      selectInput("var", 
                  label = "Choose a variable to display",
                  choices = c("Percent White", 
                              "Percent Black",
                              "Percent Hispanic", 
                              "Percent Asian"),
                  selected = "Percent White"),
      
      sliderInput("range", 
                  label = "Range of interest:",
                  min = 0, max = 100, value = c(0, 100))
    ),
    
    mainPanel(
      textOutput("selected_var"),
      textOutput("min_max")
    )
  )
)

server <- function(input, output) {
  
  output$selected_var <- renderText({ 
    paste("You have selected", input$var)
  })
  
  output$min_max <- renderText({ 
    paste("You have chosen a range that goes from",
          input$range[1], "to", input$range[2])
  })
  
}

shinyApp(ui, server)
```

