---
title: "Interactivity"
output:
  html_document:
    toc: yes
    theme: lumen 
    #number_sections: yes
    code_folding: hide
    toc_depth: 2
    toc_float: yes
    code_download: true
    #css: slides/www/style.css
  html_notebook:
   toc: yes
   theme: lumen 
   #number_sections: yes
   code_folding: hide
   toc_depth: 3
   toc_float: yes
editor_options:
  markdown:
    wrap: 140
---


# Interactive Data Visualization Frameworks
There are various ways to create interactive visualizations. We present two very popular packages, that adapt ggplots syntax, making them very comfortable to use. 

## Plots {.tabset .tabset-pills}
### plotly

Ther are two ways to make use of plotlys framework.  

[ggplotly](https://plotly.com/ggplot2/) & [plotly for R](https://plotly.com/r/)
ggplotly turns your ggplot graphs with the function *ggplotly()* into an interactive graph. 

plotly uses a different syntax style, but provides more interactive capabilities

```{r echo=TRUE, message=FALSE, warning=FALSE, size= "100%"}
library(plotly)
library(broom)
library(dplyr)
data(diamonds, package = "ggplot2")

data <- sample_n(diamonds, 300)

modlss <- loess(price ~ carat, data = data)
fit <- arrange(augment(modlss,se_fit = TRUE), carat)

p <- ggplot(NULL, mapping = aes(x = carat, y = price )) +
              geom_ribbon(data  = fit, mapping = aes(ymin = .fitted - 2*.se.fit, ymax = .fitted + 2*.se.fit), fill = "grey70")+
              geom_point(data = data, alpha = 0.7, mapping = aes(size = depth, group = cut, color = cut)) +
              geom_line(data = fit, aes(x = carat, y = .fitted)) 
  


ggplotly(p) %>%
  layout(legend = list(x = 0.1, y = 0.9))
```

 
### highcharter 

The main difference in ggplot2's geom_ functions and hc_add_series is that we need to add data and aesthetics explicitly in every function while in ggplot2 one can add data and aesthetics in a layer and then can further add more geoms which can work on same data and aesthetics.

An accurate example is given below using the diamond dataset in the ggplot2 package.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(highcharter)
library(broom)
library(dplyr)
data(diamonds, package = "ggplot2")

data <- sample_n(diamonds, 300)

modlss <- loess(price ~ carat, data = data)
fit <- arrange(augment(modlss,se_fit = TRUE), carat)

highchart() %>%
  hc_plotOptions(bubble = list(minSize = 1, maxSize = 20)) %>% hc_add_series(fit, type = "arearange",
                hcaes(x = carat, low = .fitted - 2*.se.fit,
                      high = .fitted + 2*.se.fit),
                linkedTo = "fit") %>%
  hc_add_series(data, type = "scatter",
                hcaes(x = carat, y = price, size = depth, group = cut)) %>%
  hc_add_series(fit, type = "line", hcaes(x = carat, y = .fitted),
                name = "Fit", id = "fit")
 
```

### plot_ly 

The main difference in ggplot2's geom_ functions and hc_add_series is that we need to add data and aesthetics explicitly in every function while in ggplot2 one can add data and aesthetics in a layer and then can further add more geoms which can work on same data and aesthetics.

An accurate example is given below using the diamond dataset in the ggplot2 package.

```{r echo=TRUE, message=FALSE, warning=FALSE, out.width="100%", fig.align='center'}
library(plotly)
library(broom)
library(dplyr)
library(shiny)
data(diamonds, package = "ggplot2")

data <- sample_n(diamonds, 300)

modlss <- loess(price ~ carat, data = data)
fit <- augment(modlss, se_fit = TRUE)


plot_ly(data = data, x = ~carat, width = 700,
    height = 500) %>% 
  add_markers(y = ~price, 
              color = ~cut, 
              size = ~carat, 
              text = ~paste("Price: ", price, '$<br>Cut:', cut)) %>%
  add_lines(y = ~fitted(loess(price ~ carat)),
                         line = list(color = 'lightblue'),
                         name = "Loess Smoother") %>%
  add_ribbons(data = augment(loess(price ~ carat,data = data),se_fit = TRUE), 
              ymin = ~.fitted - 2 * .se.fit,
              ymax = ~.fitted + 2 * .se.fit,
              line = list(color = "rgba(2, 162, 182, 0.05)"),
              fillcolor = "rgba(2, 162, 182, 0.2)",
              name = "Standarderror"
              ) %>%
  layout(legend = list(x = 0.1, y = 0.9))

```

## Maps

The [leaflet](https://rstudio.github.io/leaflet/) package is a very popular framework to create interactive maps.  

```{r}
library(leaflet)
leaflet() %>%
  setView(lng= 5.94852, lat= 49.50437, zoom = 16) %>% 
  addTiles() %>%
  addMarkers(lng= 5.94852, lat= 49.50437,  popup = "Interactive Data Viz Course") 
```



## Data tables



```{r}
library(DT)
data(diamonds, package = "ggplot2") # load data 

data <- diamonds[sample(nrow(diamonds), 300),1:5] #create a subset of the dataset

datatable(data, filter = 'top',  
          options = list(   searchHighlight = TRUE, pageLength = 15 ))

```
## Slides 

Using ioslides we can also implement interactive plots in our presentations! 

```{r eval = FALSE}
---
title: Do Natural Disasters Stimulate Environmental Attitudes? Evidence from a Natural
  Experiment.
author: "Hamid Bulut"
date: "27/4/2022"
output:
  ioslides_presentation:
    css: www/styles.css
    widescreen: yes
    smaller: yes
    highlight: monochrome
  slidy_presentation:
    highlight: monochrome
  beamer_presentation:
    highlight: monochrome
subtitle: A Regression Discontinuity Design Analysis
editor_options:
  markdown:
    wrap: 72
---
```




# Publish R Markdown documents on RPubs

https://rpubs.com/

# R Markdown Syntax

https://bookdown.org/yihui/rmarkdown/markdown-syntax.html


# Shiny

https://rpubs.com/odenipinedo/building-web-applications-with-Shiny-in-R


